Multi sky-view\\ 3D aerosol distribution recovery

### 2013-10-02 article.tex
modifications to the graphics
bookmark

\usepackage{opex3}
\usepackage{times}
\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{bm}
\usepackage{enumerate}
\usepackage[]{todonotes} % Add option [disable] to hide all todo notes.
\usepackage{xfrac}
\usepackage{paralist}
\usepackage{cite}
\usepackage{soul}
\usepackage{layouts}

@@

@@

\noindent{\bf Forward models and distributions}: 
\Cref{fig:results} shows estimation results, corresponding to the
original distributions of \cref{fig:distributions}.
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/results}}
  \caption{\small Reconstructions of the scenes shown in
    \cref{fig:distributions}. Color represents aerosol density. The
    density units are $10^{6}~{\rm particles}/{\rm m}^3.$ In [a,b],
    single-scattering simulated images are used as input to the
    recovery.  In [c,d], MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
\hl{
In these simulations the atmosphere domain was defined over a
$20\times20 \times 40$ grid. Thirty six cameras were placed
$\sim7$km apart on a $6\times6$ grid.
}
In Figs.~\ref{fig:results}(a) and (b), the single-scattering model was
used both in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}(c) and (d), the MC model (multiple scattering)
rendered the raw images, over which the estimation algorithm
ran. Overall, the distributions, the density order of magnitude and
values are consistent.
Errors in Figs.~\ref{fig:results}(a) and (b) stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
the algorithm of \cref{sec:inverse-problem}.
The overall mass is recovered, but for 6.5\% loss. \\

@@

\noindent{\bf Aerosol characteristics}: We used the {\em Haze blobs} scene, but varied the  
aerosol characteristics. Compared to the aerosol described in Sec.~\ref{sec:simul}, we tested two variations. In one variation, the phase function was isotropic, i.e., 
$[g_{\rm R},g_{\rm G},g_{\rm B}]=[0,0,0]$. In the other variation, the aerosol is partly absorbing: its single scattering albedo per color channel is 
$[\varpi^{\rm aerosol}_{\rm R},\varpi^{\rm aerosol}_{\rm G},\varpi^{\rm aerosol}_{\rm B}]=
[0.69,0.74,0.78]$.  All rendered images used MC, and recovery used $N_{\rm views}=36$.
Sample results are shown in Fig.~\ref{fig:variations}(a,b,c,d) and in Table~\ref{tbl:mass}.\\

\noindent{\bf Density scale}: We used the aerosol {\em Haze blobs} distribution and characteristics as described in Sec.~\ref{sec:simul}, but increased the aerosol density tenfold everywhere. This significantly increases the effects of high order scattering, as shown in Fig.~\ref{fig:cross_sections}(b) and Fig.~\ref{fig:variations}(e). Consequently, $\epsilon$ increases, when using $N_{\rm views}=36$. Still, Fig.~\ref{fig:variations}(f) shows that the spatial distribution outlines are recovered similarly to the other tests.

%\hl{Thickening the aerosols density ten folds in the} {\em Haze Blobs} \hl{scene
%resulted in a larger local error, i.e. $\epsilon=0.98$ (compared to $\epsilon=0.65$).
%This admits to the fact that the single-scattering model, on which the reconstruction
%algorithm is based, is valid when the optical depth of the medium is small.}
% \begin{figure}[h]
%   \centering
%   \yoavcomment{\includegraphics{images/high_density_results.pdf}}
%   \caption{\small (a) and (b) show MC simulations of low and
%     high density scenes, respectively. (c) shows the reconstruction of
%     the high density scene.}
%   \label{fig:high_density}
% \end{figure}

>>>>

\usepackage{opex3}
\usepackage{times}
\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{bm}
\usepackage{enumerate}
\usepackage[]{todonotes} % Add option [disable] to hide all todo notes.
\usepackage{xfrac}
\usepackage{paralist}
\usepackage{cite}
\usepackage{soul}
\usepackage{layouts}
\usepackage{booktabs}
\usepackage{colortbl}

@@

\definecolor{Gray}{gray}{0.9}

@@

\noindent{\bf Forward models and distributions}: 
\Cref{fig:results} shows estimation results, corresponding to the
original distributions of \cref{fig:distributions}.
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/results}}
  \caption{\small Reconstructions of the scenes shown in
    \cref{fig:distributions}. Color represents aerosol density. The
    density units are $10^{6}~{\rm particles}/{\rm m}^3.$ In [a,b],
    single-scattering simulated images are used as input to the
    recovery.  In [c,d], MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
\hl{
In these simulations the atmosphere domain was defined over a
$20\times20 \times 40$ grid. Thirty six cameras were placed
$\sim7$km apart on a $6\times6$ grid.
}
In Figs.~\ref{fig:results}(a) and (b), the single-scattering model was
used both in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}(c) and (d), the MC model (multiple scattering)
rendered the raw images, over which the estimation algorithm
ran. Overall, the distributions, the density order of magnitude and
values are consistent.
Errors in Figs.~\ref{fig:results}(a) and (b) stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
the algorithm of \cref{sec:inverse-problem}.
The overall mass is recovered, but for 6.5\% loss. \\

@@

\noindent{\bf Aerosol characteristics}: We used the {\em Haze blobs} scene, but varied the  
aerosol characteristics. Compared to the aerosol described in \cref{sec:simul}, we tested two variations. In one variation, the phase function was isotropic, i.e., 
$[g_{\rm R},g_{\rm G},g_{\rm B}]=[0,0,0]$. In the other variation, the aerosol is partly absorbing: its single scattering albedo per color channel is 
$[\varpi^{\rm aerosol}_{\rm R},\varpi^{\rm aerosol}_{\rm G},\varpi^{\rm aerosol}_{\rm B}]=
[0.69,0.74,0.78]$.  All rendered images used MC, and recovery used $N_{\rm views}=36$.
Sample results are shown in Figs.~\ref{fig:simulation_particles}(a)--(d) and in Table~\ref{tbl:mass}.\\

\newcolumntype{g}{>{\columncolor{Gray}}r}
\begin{table}[htbp]
  \centering
  \begin{tabular}{cccccg}
    \toprule
    Haze Scene & Forward Model& Density & Isotropic PF & Absorbing & $\epsilon$ \\
    \midrule
    Front & Single & Low & & & 0.18 \\
     & MC & Low & & & 0.65 \\
    \cmidrule(r){1-5}
    Blobs & Single & Low & & & 0.14 \\
     & MC & Low & & & 0.65 \\
     & MC & Low & $\surd$  & & 0.49 \\
     & MC & Low & & $\surd$ & 0.83 \\
     & MC & High & & & 0.98 \\
    \bottomrule
  \end{tabular}
  \caption{Local error for the various simulations}
  \label{tbl:mass}
\end{table}

\noindent{\bf Density scale}: We used the aerosol {\em Haze blobs} distribution
and characteristics as described in Sec.~\ref{sec:simul}, but increased the
aerosol density tenfold everywhere. This significantly increases the effects
of high order scattering, as shown in \cref{fig:cross_sections}(b) and
\cref{fig:simulation_particles}(c). Consequently, $\epsilon$ increases,
when using $N_{\rm views}=36$. Still, \cref{fig:reconstructions}(c) shows
that the spatial distribution outlines are recovered similarly to the other
tests.

%\hl{Thickening the aerosols density ten folds in the} {\em Haze Blobs} \hl{scene
%resulted in a larger local error, i.e. $\epsilon=0.98$ (compared to $\epsilon=0.65$).
%This admits to the fact that the single-scattering model, on which the reconstruction
%algorithm is based, is valid when the optical depth of the medium is small.}
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/simulation_particles.pdf}}
  \caption{\small (a) and (b) show MC simulations of low and
    high density scenes, respectively. (c) shows the reconstruction of
    the high density scene.}
  \label{fig:simulation_particles}
\end{figure}
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/reconstructions.pdf}}
  \caption{\small (a) and (b) show MC simulations of low and
    high density scenes, respectively. (c) shows the reconstruction of
    the high density scene.}
  \label{fig:reconstructions}
\end{figure}
